Fermi and eROSITA bubbles

### 2021-12-17 paper.tex
update

\documentclass[twocolumn]{aastex631}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{url}
\usepackage{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

@@

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\begin{tabular}{@{}llc@{}}
\toprule
Parameter                           & Description                   & Value                         \\ \midrule
Potential \& halo                   &                               &                               \\
$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge  & 100 km/s                      \\
$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$ \\
$v_{\text{halo}}$                   &                               & 131.5 km/s                    \\
$d_{\text{h}}$                      &                               & 12 kpc                        \\
Atmosphere                          &                               &                               \\
$T_{\text{\text{atmp}}}$            &                               & $10^{6}$ K                    \\
Disk                                &                               &                               \\
$z_{0}$                             & Scale height of disk          & 100 pc                        \\
$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk   & $6\text{ c.c.}^{-1}$          \\
$T_{\text{\text{disk}}}$            & Temperature of disk           & $10^{3}$ K                    \\ \bottomrule
\end{tabular}
\end{table*}

@@

\item Clumpy cold disk:
  \begin{enumerate}
    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{paek-ism-density}
    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{paek-ism-density}
    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{paek-ism-density}
    \item Average mass density:
          \begin{equation}
             \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right].
             \label{disk-density}
          \end{equation}

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{xcolor,colortbl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{url}
\usepackage{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

@@

\definecolor{Gray}{gray}{0.85}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrr@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                           & Description                   & Value                                & Reference                         \\ \midrule
{\bf Potential \& halo}             &                               &                                      &                                   \\ \cmidrule(r){1-1}
$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge  & 100 km/s                             & \citep{velocity-dispersion-MW}    \\
$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$        &                                   \\
$v_{\text{halo}}$                   &                               & 131.5 km/s                           & \citep{Johnston1995}              \\
$d_{\text{h}}$                      &                               & 12 kpc                               & \citep{Johnston1995}              \\
{\bf Atmosphere}                    &                               &                                      &                                   \\ \cmidrule(r){1-1}
$T_{\text{\text{atmp}}}$            &                               & $10^{6}$ K                           & \citep{temperature-MW}            \\
{\bf Disk}                          &                               &                                      &                                   \\ \cmidrule(r){1-1}
$z_{0}$                             & Scale height of disk          & 100 pc                               &                                   \\
		$\rho_{\text{disk}}^{\text{peak}}$  & Peak number density of disk   & $6\text{ c.c.}^{-1}$ & \citep{peak-ism-density}          \\
$T_{\text{\text{disk}}}$            & Temperature of disk           & $10^{3}$ K                           &                                   \\ \midrule
\end{tabular}
\end{table*}

@@

\item Clumpy cold disk:
  \begin{enumerate}
    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{peak-ism-density}
    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{peak-ism-density}
    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{peak-ism-density}
    \item Average mass density:
          \begin{equation}
             \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right].
             \label{disk-density}
          \end{equation}
